Synthesizing Symmetric Lenses

### 2019-02-25 papers/SymmetricLenses/main.tex
minor typo
add minor fixes

\noindent
In today's data-rich world, similar information is often
stored in different places and in different formats. For instance, electronic
calendars come in iCalendar, vCalendar, and h-event
formats~\cite{calendar-formats}; US taxation data can be transmitted via Tax
XML (used by the US government for e-filing) or TXF (used by
TurboTax)~\cite{tax-formats}; and sewing machines can use embroidery files
in formats with names like PES, DST, and several
others~\cite{embroidery-formats}.
%
\bcp{I'm not satisfied with the embroidery example: It doesn't obviously
  correspond to a bidirectional situation (the sewing machine does not need
  to send back the embroidery file to anybody).  The tax example could be
  criticized on the same grounds.}
\afm{I still think that there are situations where the embroidery file makes
  sense (I'm sharing my design with a friend, who then tweaks it and sends it
  back. There may also need to file-specific information, where one contains
  parameters like how fast to embroider and some doesn't, to be honest I don't
  know much about embroidery though. Thinking about other examples, however.)}

@@

How can we identify such a ``likely'' lens? We propose the following heuristic:
A satisfying lens is ``more likely'' if it u;ses more data from one format to
construct the other. One manifestation of this principle involves choosing the
identity lens (which uses all the data) rather than the disconnect lens (which
uses none of the data). We define the likelihood of a satisfying lens as the
expected number of bits required to recover data in one format from synchronized
data in the other. Higher likelihoods correspond to fewer bits. We say that two
strings $s$ and $t$ are \emph{synchronized according to lens $l$} if $l.\PutR\
s\ t = t$ and $l.\PutL\ t\ s = s$. We say that we can \emph{recover} $s$ from
$t$ using bits $b$ and lens $l$ if we can reconstruct $s$ from $t$, $b$, and
$l$. For example, given the \IdentityLens{} lens, we can recover $s$ from $t$
using no bits because, in this case, $s$ is just $t$. In contrast, given the
\Disconnect{} lens, we need enough bits to fully encode $s$ in order to recover
it from $t$ because $t$ contains no useful information. Thus, if both
\IdentityLens{} and \Disconnect{} are satisfying lenses for a particular pair of
formats, then \IdentityLens{} will be more likely.

@@

All three sources provide realistic problems suitable for
answering the research questions: Flash Fill data cleaning tasks are either
derived from online help forums or taken from the Excel product team; Augeas is
a utility that transforms Linux configuration files into a manageable dictionary
form; and many of the remaining benchmarks arise from synchronizing real-world
data formats such as BibTeX and EndNote.  Each task consists of a source and
target regular expression.\saz{Do we want to say anything about the sizes of these?}

>>>>

\noindent
In today's data-rich world, similar information is often stored in different
places and in different formats. For instance, electronic calendars come in
iCalendar, vCalendar, and h-event formats~\cite{calendar-formats}; US taxation
data can be transmitted via Tax XML (used by the US government for e-filing) or
TXF (used by TurboTax)~\cite{tax-formats}; configuration files can be stored in
ad-hoc or structured file formats~\cite{augeas} (for example, scheduled commands
can be stored in a crontab or as Windows's Scheduled Tasks xml).

@@

How can we identify such a ``likely'' lens? We propose the following heuristic:
A satisfying lens is ``more likely'' if it uses more data from one format to
construct the other. One manifestation of this principle involves choosing the
identity lens (which uses all the data) rather than the disconnect lens (which
uses none of the data). We define the likelihood of a satisfying lens as the
expected number of bits required to recover data in one format from synchronized
data in the other. Higher likelihoods correspond to fewer bits. We say that two
strings $s$ and $t$ are \emph{synchronized according to lens $l$} if $l.\PutR\
s\ t = t$ and $l.\PutL\ t\ s = s$. We say that we can \emph{recover} $s$ from
$t$ using bits $b$ and lens $l$ if we can reconstruct $s$ from $t$, $b$, and
$l$. For example, given the \IdentityLens{} lens, we can recover $s$ from $t$
using no bits because, in this case, $s$ is just $t$. In contrast, given the
\Disconnect{} lens, we need enough bits to fully encode $s$ in order to recover
it from $t$ because $t$ contains no useful information. Thus, if both
\IdentityLens{} and \Disconnect{} are satisfying lenses for a particular pair of
formats, then \IdentityLens{} will be more likely.

@@

All three sources provide realistic problems suitable for answering the research
questions: Flash Fill data cleaning tasks are either derived from online help
forums or taken from the Excel product team; Augeas is a utility that transforms
Linux configuration files into a manageable dictionary form; and many of the
remaining benchmarks arise from synchronizing real-world data formats such as
BibTeX and EndNote. Each task consists of a source and target regular
expression. These tasks can be quite quite large, as we are synthesizing complex
transformations between real file formats -- some of the lenses and
specifications are over 500 AST nodes.
